Annotated metamodel for MSR course papers

### 2015-08-06 presentations/paper/paper.tex
Add an abstract for the paper

\begin{abstract}
  This should be 100-200 words. Use present or past tense, but use it
  consistently. Prefer ``we'' over ``I'' here and throughout the
  paper. The abstract should summarize the methodology and results;
  see the corresponding sections below. Your paper is preferably
  typeset with LaTeX and it should comply with the Springer LNCS
  style. (That style is also available for word users.) 
\end{abstract}

>>>>

\begin{abstract}
  In 2014, the Git surpassed Subversion as the top code management tool \cite{EComSurv14}. With so many authors colaborating comes the need for a appropriate and standardized use of elemental actions like doing commits. Although the official Git documentation states very clear guidelines \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or simply ignore them.
  This paper presents a tool that analyzes a set of commits regarding criteria composed of the official guidelines and some common mistakes, and shows a prototypical website that encourages improvements in commit-etiquette by creating a competitive score-board for a given GitHub repository. We also perform a machine learning powered analysis of correlations between all criteria.

  This should be 100-200 words. Use present or past tense, but use it
  consistently. Prefer ``we'' over ``I'' here and throughout the
  paper. The abstract should summarize the methodology and results;
  see the corresponding sections below. Your paper is preferably
  typeset with LaTeX and it should comply with the Springer LNCS
  style. (That style is also available for word users.)
\end{abstract}
